Rule-Based Normalization of German Twitter Messages

### 2013-08-15 darmstadt_gscl_2013/article_twitter_normalization.tex
minor changes

This confusion is explained by the fact that the above classifications
both rely on several independent criteria at the same time, however
each of these criteria characterizes an NTN system from a different
point of view. As a consequence of this, unambiguous assignment of an
NTN approach to one particular class often becomes impossible. In
order to avoid this, we instead suggest using separate classifications
for each type of involved characterizing criterion.

@@

In order to estimate the percentage of unknown words in Twitter
messages, we randomly selected 10,000 tweets from a previously
collected corpus, split them into sentences and tokenized using social
media-aware tokenizer by Christopher Potts
\footnote{\url{http://sentiment.christopherpotts.net/code-data/happyfuntokenizing.py}}.
After skipping all words which did not contain any alphabetic
characters or consisted only of a single letter, we obtained a list of
129,146 tokens. As reference systems for dictionary lookup we used
open-source spell checking program \texttt{hunspell}\footnote{Ispell
  Version 3.2.06 (Hunspell Version 1.3.2); dictionary de\_DE.} and
publicly available part-of-speech tagger
\texttt{TreeTagger}\footnote{Version 3.2 with German parameter file
  UTF-8.} (Schmid, \cite{schmid}).

@@

We classified found OOV tokens into the following three groups
according to the reasons why these tokens could have been omitted from
corresponding applications' dictionaries:
\begin{enumerate}
  \item \textbf{Objective limitedness of machine-readable dictionaries
    (MRD)}. Among this group, we counted words of basic vocabulary
    which did not get into applications' MRD either because they
    supposedly were rare or did not exist at the time when
    dictionaries were created. Another reason for inclusion in this
    type was the belonging of a word to an open lexical or
    part-of-speech class (like, for example, named entities or
    interjections) which are often omitted from MRDs due to the
    impossibility to fully cover them;\label{dict}
  \item \textbf{Sloppiness of users' input}. In the scope of this
    second group, we considered incorrect spellings of words
    encountered in text;\label{spell}
  \item \textbf{Stylistic specifics of text genre}. This group
    comprised words which could be considered as illegal from the
    point of view of standard language but were perfectly valid terms
    in the domain of web discourse or more specifically in Twitter
    communication.\label{style}
\end{enumerate}

@@

In Table \ref{table:mrd}, percentage figures for each of the above
subgroups are shown. We have considered OOV-distributions for both
\texttt{hunspell} and \texttt{TreeTagger}. For each of them, we
estimated the percentage of a particular subclass with regard to the
total number of occurrences of all OOV-tokens (column ``\totaloov{}'')
as well as with regard to their percentage rate in the list of only
unique OOVs disregarding frequencies (column ``\uniqoov{}'').
\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``Objective limitedness of MRD''\label{table:mrd}}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    regular German words & 7.82 & 8.78 & 2.8 & 3.49\\
    compounds & 1.21 & 2.42 & 2.51 & 4.55\\
    abbreviations & 3.98 & 4.77 & 3.27 & 3.44\\
    interjections & 5.95 & 4.54 & 5.58 & 4.29\\
    person names & 4.73 & 6.41 & 2.32 & 3.47\\
    geographic locations & 1.5 & 2.53 & 1.16 & 1.88\\
    company names & 2.27 & 2.84 & 4.35 & 3.01\\
    product names & 2.13 & 2.57 & 2.45 & 3.23\\
    newly coined terms & 1.35 & 1.31 & 3.33 & 2.38\\
    loanwords & 3.68 & 4.03 & 3.29 & 2.87\\
    foreign words & 11.5 & 13.76 &  9.57 & 10.91\\\hline
    {\bfseries total} & 46.12 & 53.96 & 40.63 & 43.52\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

Similarly to class \ref{dict}, we subdivided the group ``Sloppiness of
users' input'' into the following subgroups:
\begin{enumerate}
  \item insertions, e.g. \textit{dennen} instead of \textit{denen};
  \item deletions, e.g. \textit{scho} instead of \textit{schon};
  \item substitutions, e.g. \textit{fur} instead of \textit{f\"ur};
\end{enumerate}
according to the type of operation which led to a particular spelling
mistake. In cases when multiple different operations were involved
simultaneously, we explicitly marked each of these operations in our
data. Statistical distribution of these subclasses is shown in Table
\ref{table:spell}.
\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``Sloppiness of users' input''\label{table:spell}}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    insertions & 0.49 & 1 & 0.18 & 0.34 \\
    deletions & 8.44 & 6.38 & 6.52 & 5.27 \\
    substitutions & 2.17 & 3.37 & 1.11 & 1.2 \\\hline
    {\bfseries total} & 11.1 & 10.75 & 7.81 & 6.81\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

%% As is clear from the table, deletions are by far the most common type
%% of misspellings. The reasons for that are either relatively frequent
%% omissions of characters made by users or even more often automatic
%% truncations of too long messages which are performed by Twitter
%% service itself.\footnote{As is generally known, Twitter imposes a
%%   strong restriction on the length of posted messages which can be no
%%   longer than 140 characters. Upon exceeding this length, tweets get
%%   automatically truncated to the maximal allowed length.}

Finally, the third group -- ``Stylistic specifics of text genre'' --
was subdivided into the subgroups:
\begin{enumerate}
  \item @-tokens, e.g. \textit{@ZDFonline}, \textit{@sechsdreinuller};
  \item hashtags, e.g. \textit{\#Kleinanzeigen}, \textit{\#wetter};
  \item links, e.g. \textit{http://t.co}, \textit{sueddeutsche.de};
  \item smileys, e.g. \textit{:-P}, \textit{xD};
  \item slang, e.g. \textit{OMG}, \textit{WTF} etc.
\end{enumerate}
according to the formal or lexical class which the tokens belonged
to. Additionally, we also considered as \textit{slang} spelling
variants of standard language words which could be regarded as their
colloquial equivalents. Such words included cases like, for example,
\textit{ned} instead of \textit{nicht} or \textit{grad} instead of
\textit{gerade}, and were marked both as \textit{misspelling}s and
\textit{slang} in our classification. A detailed statistics on the
subgroups of class 3 is shown in Table \ref{table:style}:
\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``Stylistic specifics of text genre''\label{table:style}}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    @-tokens & 13.02 & 20.23 & 16.19 & 21.91\\
    hashtags & 7.35 & 6.18 & 13.06 & 10.59\\
    links & 2.43 & 0.4 & 4.89 & 6.07\\
    smileys & 2 & 0.73 & 6.88 & 1.2\\
    slang & 16.22 & 5.27 & 6.94 & 4.77\\\hline
    {\bfseries total} & 41.02 & 32.81 & 47.96 & 44.54\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

A striking outlier of 16.22~\% for slang tokens in column 1 of the
Table is explained by the fact that the word ``RT'' which occurred
1,235 times in our texts and was by far the most frequent OOV in
analyzed data set, was recognized as out-of-vocabulary by
\texttt{hunspell} but was not deemed as such by
\texttt{TreeTagger}. Luckily, such singleton cases were rather rare
exceptions during the analyses and did not affect much the remaining
classes of OOVs, so that distributions of unknown tokens for both
tools were more or less similar or at least comparable to a certain
extent.

However, an even more important conclusion which can be drawn from the
analyzed data is the fact that for both \texttt{TreeTagger} and
\texttt{hunspell}, Twitter-specific phenomena like special tokens,
colloquial expressions or sloppily typed words accounted for more than
a half of all unknown words found during the analysis. Since different
classes of these Twitter phenomena were formed by different processes
and also have different degrees of ambiguity, we will suggest
different normalization procedures for each of them in the next
Section.

@@

\subsection{Replacement of Twitter-Specific Phenomena}
According to Parker (\cite{parker}), hasthags were presumably introduced by
Chris Messina, a renowned advocate of open-source community, in August
2007. The ``hash godfather'', as Messina describes himself, allegedly borrowed
the idea of marking relevant topics with the ``\#''- sign from Internet Relay
Chats (IRC) -- the forebears of modern social networks -- which have been
using the pound character for marking their channel names since the early
1990s.

Luckily for us, this Messina's ``novelty'' brought along a strict formal
feature by which future hashtags could be identified. Other types of words
which also are usually considered as OOVs in Twitter but have unambiguous
formal traits are at-tokens, hyperlinks, e-mail addresses, and smileys. The
presence of such formal criteria suggests that these classes could best be
handled by rule-based methods and namely finite-state techniques like
finite-state transducers (FST) (cf. Jurafsky and Martin, \cite{jurafsky},
pp.57-60).

For our purposes, we developed a prototypic Python system analogous to
an FST in which a set of regular expressions was associated with
corresponding actions performed on matched subgroups. If some rules'
subgroups clashed together on certain contexts, a set of special
criteria was used to determine which rule had to be preferred. These
criteria involved length of text spans matched by subgroups, length of
left and right context mathced by corresponding regular expressions,
and, finally, the order in which these expressions appeared in rule
file.

In our system, unambiguous tokens like, for example, e-mail addresses were
replaced with an artificial word ``\%Mail''. Emoticons were substituted by
tokens ``\%PosSmiley'' or ``\%NegSmiley'' depending on the type of emotion
presumably conveyed by these expressions. In cases when an emoticon was
ambiguous with regard to its polarity, it was replaced with the special word
``\%Smiley''. Furthermore, leading ``\#{}'' characters were stripped off from
the beginning of hashtags thus leaving only the alphabetic part of these
tokens.

A more complicated case turned out to be the at-tokens and hyperlinks. For
them, we had to disambiguate whether these words played an important syntactic
role in sentence or not. In the former case, these words were replaced with
artificial counterparts. In the latter case, such words were deleted from
sentence in order not to confuse further intended parsing processing.

Precision, recall and F1 metrics for replacement of Twitter-specific phenomena
are shown in Table \ref{table:tw-phenomen-metrics}.

\begin{table}
  \caption{Precision, recall and F1 score for replacement of
    Twitter-specific phenomena\label{table:tw-phenomen-metrics}}
  \begin{tabular}{*{4}{>{\centering\arraybackslash}p{0.25\textwidth}}}
    \hline\noalign{\smallskip}
    OOV subclass & Precision & Recall & F1 score\\\hline
    attoken & 98.87 & 98.87 & 98.87\\
    link & 99.44 & 100.00 & 99.72\\
    smiley & 93.79 & 76.26 & 84.12\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

All the artificial words were added to custom user dictionaries of
\texttt{TreeTagger} and \texttt{hunspell}. For tagging, we assigned NE tags to
all artificial tokens with the only exception of emoticon replacements which
got the tag INJ. Furthermore, positions and lengths of all replacements we
remembered along with the original words which were replaced, and a
restoration step to original forms was performed for user names after tagging.

@@

As can be seen from the figures, both kinds of spelling variations have nearly
Zipfian distribution. However colloquial spelling variants, if used, tend to
be used frequently whereas non-colloquial misspellings are rather represented
by sporadic singletons. This could be explained by the fact that colloquial
spellings are usually formed by systematic rewriting processes. These
processes are supposed to make written form of words more similar to their
casual soundings in everyday speech. According to our data, the most
productive of such processes were:
\begin{itemize}
  \item Omissions of `e' in unstressed (``schwa'') positions,
    e.g. \textit{w\"urd}, \textit{zuguckn} etc. In cases when `e' was part of
    the impersonal pronoun ``es'' following a verb, remaining `s' of this
    pronoun was usually appended to the preceding verb form;

@@

Finally, as a first step towards an extrinsic evaluation, we measured
\texttt{TreeTagger}

@@

\section{Conclusion}\label{conclusion}

>>>>

This confusion is explained by the fact that the above classifications
both rely on several independent criteria at the same time, however
each of these criteria characterizes an NTN system from a different
point of view. As a consequence of this, unambiguous assignment of an
NTN approach to one particular class often becomes impossible. In
order to avoid this, we instead suggest using separate classifications
for each type of involved criteria.

@@

In order to estimate the percentage of unknown words in Twitter
messages, we randomly selected 10,000 tweets from a previously
collected corpus, split them into sentences and tokenized using social
media-aware tokenizer by Christopher Potts.
\footnote{\url{http://sentiment.christopherpotts.net/code-data/happyfuntokenizing.py}}
After skipping all words which did not contain any alphabetic
characters or consisted only of a single letter, we obtained a list of
129,146 tokens. As reference systems for dictionary lookup we used
open-source spell checking program \texttt{hunspell}\footnote{Ispell
  Version 3.2.06 (Hunspell Version 1.3.2); dictionary de\_DE.} and
publicly available part-of-speech tagger
\texttt{TreeTagger}\footnote{Version 3.2 with German parameter file
  UTF-8.} (Schmid, \cite{schmid}).

@@

We classified found OOV tokens into the following three groups
according to the reasons why these tokens could have been omitted from
corresponding applications' dictionaries:
\begin{enumerate}
  \item \textbf{Objective limitedness of machine-readable dictionaries
    (MRD)}. Among this group, we counted words of basic vocabulary
    which did not get into applications' MRD either because they
    supposedly were rare or did not exist at the time when
    dictionaries were created. Another reason for the inclusion in
    this type was the belonging of a word to an open lexical or
    part-of-speech class (like, for example, named entities or
    interjections) which are often omitted from MRDs due to the
    impossibility to fully cover them;\label{dict}
  \item \textbf{Stylistic specifics of text genre}. This group
    comprised words which could be considered as illegal from the
    point of view of standard language but were perfectly valid terms
    in the domain of web discourse or more specifically in Twitter
    communication;\label{style}
  \item \textbf{Sloppiness of users' input}. In the scope of this
    group, we considered incorrect spellings of words encountered in
    text.\label{spell}
\end{enumerate}

@@

In Table \ref{table:mrd} on Page \pageref{table:mrd}, percentage
figures for each of the above subgroups are shown. We have considered
OOV-distributions for both \texttt{hunspell} and
\texttt{TreeTagger}. For each of them, we estimated the percentage of
a particular subclass with regard to the total number of occurrences
of all OOVs (column ``\totaloov{}'') as well as with regard to their
percentage rate in the list of only unique unknown tokens disregarding
their frequencies (column ``\uniqoov{}'').
\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``Objective limitedness of MRD''\label{table:mrd}}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    regular German words & 7.82 & 8.78 & 2.8 & 3.49\\
    compounds & 1.21 & 2.42 & 2.51 & 4.55\\
    abbreviations & 3.98 & 4.77 & 3.27 & 3.44\\
    interjections & 5.95 & 4.54 & 5.58 & 4.29\\
    person names & 4.73 & 6.41 & 2.32 & 3.47\\
    geographic locations & 1.5 & 2.53 & 1.16 & 1.88\\
    company names & 2.27 & 2.84 & 4.35 & 3.01\\
    product names & 2.13 & 2.57 & 2.45 & 3.23\\
    newly coined terms & 1.35 & 1.31 & 3.33 & 2.38\\
    loanwords & 3.68 & 4.03 & 3.29 & 2.87\\
    foreign words & 11.5 & 13.76 &  9.57 & 10.91\\\hline
    {\bfseries total} & 46.12 & 53.96 & 40.63 & 43.52\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

Similarly to class \ref{dict}, we subdivided the group -- ``Stylistic
specifics of text genre'' -- into the following subgroups:
\begin{enumerate}
  \item @-tokens, e.g. \textit{@ZDFonline}, \textit{@sechsdreinuller};
  \item hashtags, e.g. \textit{\#Kleinanzeigen}, \textit{\#wetter};
  \item links, e.g. \textit{http://t.co}, \textit{sueddeutsche.de};
  \item smileys, e.g. \textit{:-P}, \textit{xD};
  \item slang, e.g. \textit{OMG}, \textit{WTF} etc.
\end{enumerate}
according to the formal or lexical class which tokens of this group
belonged to. Additionally, spelling variants of standard language
words which could also be regarded as their colloquial equivalents
like, for example, \textit{ned} instead of \textit{nicht} or
\textit{grad} instead of \textit{gerade}, were considered by us both
as \textit{misspelling}s and as \textit{slang} in our
classification. A detailed statistics on the subgroups of class
\ref{style} is shown in Table \ref{table:style}:
\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``Stylistic specifics of text genre''\label{table:style}}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    @-tokens & 13.02 & 20.23 & 16.19 & 21.91\\
    hashtags & 7.35 & 6.18 & 13.06 & 10.59\\
    links & 2.43 & 0.4 & 4.89 & 6.07\\
    smileys & 2 & 0.73 & 6.88 & 1.2\\
    slang & 16.22 & 5.27 & 6.94 & 4.77\\\hline
    {\bfseries total} & 41.02 & 32.81 & 47.96 & 44.54\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

A striking outlier of 16.22~\% for slang tokens in column 1 of the
Table is explained by the fact that the word ``RT'' which occurred
1,235 times in our texts and was by far the most frequent OOV in
analyzed data set, was recognized as out-of-vocabulary by
\texttt{hunspell} but was not deemed as such by \texttt{TreeTagger}.

Finally, the last group -- ``Sloppiness of users' input'' -- was split
into the following subclasses:
\begin{enumerate}
  \item insertions, e.g. \textit{dennen} instead of \textit{denen};
  \item deletions, e.g. \textit{scho} instead of \textit{schon};
  \item substitutions, e.g. \textit{fur} instead of \textit{f\"ur};
\end{enumerate}
according to the type of operation which led to a particular spelling
mistake. In cases when multiple different operations were involved
simultaneously on one word, we explicitly marked each of these
operations in our data. Statistical distribution of these subclasses
is shown in Table \ref{table:spell}.
\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``Sloppiness of users' input''\label{table:spell}}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    insertions & 0.49 & 1 & 0.18 & 0.34 \\
    deletions & 8.44 & 6.38 & 6.52 & 5.27 \\
    substitutions & 2.17 & 3.37 & 1.11 & 1.2 \\\hline
    {\bfseries total} & 11.1 & 10.75 & 7.81 & 6.81\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

As is clear from the Table, deletions are by far the most common type
of misspellings. The reasons for that are either relatively frequent
omissions of characters made by users or even more often automatic
truncations of too long messages which are performed by Twitter
service itself.\footnote{As is generally known, Twitter imposes a
  strong restriction on the length of posted messages which can be no
  longer than 140 characters. Upon exceeding this length, tweets get
  automatically truncated to the maximal allowed length.}

But an even more important conclusion that can be drawn from the
analyzed data is the fact that for both \texttt{TreeTagger} and
\texttt{hunspell}, Twitter-specific phenomena like specially marked
tokens, colloquial expressions or sloppily typed words accounted for
more than a half of all OOVs found during the analysis. And since
different classes of these Internet-based communication phenomena were
formed by different processes and also showed different degrees of
ambiguity, they should most probably be differently normalized
depending on the characteristics they show.

@@

\subsection{Replacement of Twitter-Specific Phenomena}
According to Parker (\cite{parker}), hasthags were presumably
introduced by Chris Messina, a renowned advocate of open-source
community, in August 2007. The ``hash godfather'', as Messina calls
himself, allegedly borrowed the idea of marking relevant topics in
messages with the ``\#''- sign from Internet Relay Chats (IRC) -- the
forebears of modern social networks -- which have been using the pound
character for marking their channel names since the early 1990s.

Luckily for us, this markup ``novelty'' brought along a strict formal
feature by which future hashtags could be identified. Other types of
words which are also usually considered as OOVs in Twitter but have
unambiguous traits in their written form are at-tokens, hyperlinks,
e-mail addresses, and smileys. The presence of such formal criteria
suggests that these classes could best be handled by rule-based
methods and namely finite-state techniques like finite-state
transducers (FST) (cf. Jurafsky and Martin, \cite{jurafsky},
pp.57-60).

For our purposes, we developed a prototypic Python system analogous to
an FST in which a set of regular expressions was associated with
corresponding actions performed on matched subgroups. In this system,
unambiguous tokens like, for example, e-mail addresses were replaced
with an artificial word ``\%Mail''. Emoticons were substituted by
tokens ``\%PosSmiley'' or ``\%NegSmiley'' depending on the type of
emotion presumably conveyed by these expressions. In cases when an
emoticon was ambiguous with regard to its polarity, it was replaced
with the special word ``\%Smiley''. Furthermore, leading ``\#{}''
characters were stripped off from the beginning of hashtags thus
leaving only the alphabetic part of these tokens.

A more complicated case turned out to be the at-mentions and
hyperlinks. For them, we had to disambiguate whether these words
played an important syntactic role in sentence or could be easily
omitted without breaking the syntactic structure. In the former case,
these words were replaced with artificial counterparts. In the latter
case, such words were deleted from sentence in order not to confuse
further intended parsing processing.

We measured on 1,000 sentences how well our system could disambiguate
contexts for the two above-mentioned classes and also how well it
could recognize emoticons and assign them correct polarity. Our
estimated precision, recall and F1 metrics are shown in Table
\ref{table:tw-phenomen-metrics}.

\begin{table}
  \caption{Precision, recall and F1 score for replacement of
    Twitter-specific phenomena\label{table:tw-phenomen-metrics}}
  \begin{tabular}{*{4}{>{\centering\arraybackslash}p{0.25\textwidth}}}
    \hline\noalign{\smallskip}
    OOV subclass & Precision & Recall & F1 score\\\hline
    at-mentions & 98.87 & 98.87 & 98.87\\
    links & 99.44 & 100.00 & 99.72\\
    smileys & 93.79 & 76.26 & 84.12\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

Additionally, all the artificial words were added to custom user
dictionaries of \texttt{TreeTagger} and \texttt{hunspell}. For
tagging, we assigned NE tags to all artificial tokens with the only
exception of emoticon replacements which got the tag INJ. Furthermore,
positions and lengths of all replacements we remembered along with the
original words which were replaced, and a restoration step to original
forms was performed for user names after tagging.

@@

As can be seen from the figures, both kinds of spelling variations
have nearly Zipfian distribution. However colloquial spelling
variants, if used, tend to be used frequently whereas non-colloquial
misspellings are rather represented by sporadic singletons. This could
be explained by the fact that colloquial spellings are usually formed
by systematic rewriting processes which are also usually applied to
frequently used words. True misspellings, on the contrary, are rather
produced by occasional slips of the finger, so they neither have an
apparent system in them nor they tend to reoccur in text.

In order to investigate which processes were the most common sources
of colloquial spellings

These processes are supposed to make written form of words more
similar to their casual soundings in everyday speech.

According to our data, the most productive of such
processes were:
\begin{itemize}
  \item Omissions of `e' in unstressed (``schwa'') positions,
    e.g. \textit{w\"urd}, \textit{zuguckn} etc. In cases when `e' was part of
    the impersonal pronoun ``es'' following a verb, remaining `s' of this
    pronoun was usually appended to the preceding verb form;

@@

Finally, as a first step towards an extrinsic evaluation, we measured
how \texttt{TreeTagger} performance changed after normalization step
was applied

@@

\section{Conclusions and Future Work}\label{conclusion}
